---
title: "My first RMD"
output: html_document
---

mpg = mtcars

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Anything not in a code chunk is just text in report

# Anything not in a code chunk is just text in report

## Anything not in a code chunk is just text in report

### Anything not in a code chunk is just text in report


#### Anything not in a code chunk is just text in report

##### Anything not in a code chunk is just text in report

Anything in a code chunk is ran as code

more hashtags means smaller text. 

if i click the +c thing in the corner it adds a code chunk

include = FALSE - doesn't show the code in the report,

warning = FALSE - doesn't show the warnings R gives you about your code

echo = FALSE - don't show the code I used, but show figures

```{r, include = FALSE, echo = FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(modelr)
library(easystats)

library(kableExtra)

```


Anything past hitting enter twice won't register as space

creates a break
<br><br><br><br>


after the break


<br><br>
```{r, echo = FALSE, message = FALSE, fig.width= 10, fig.height= 3}
mpg %>%
  ggplot(aes(x = displ, y = cty)) + 
  geom_smooth()
```


Explore the mpg dataset a bit:
```{r}
mpg %>% glimpse 
print("The first 10 rows")
firstten <- mpg%>% head(10)
kable(firstten)
```


