---
title: "Final Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE, warning = FALSE)
library(tidyverse)
library(moments)
library(broom)
library(car)
library(dplyr)
library(modelr)
df <- read.csv("merged_data.csv")
```

##Does an apple a day keep the doctor away?

  Have you ever been told by your parents "an apple a day keeps the doctor away"? A lot of people were (you're not special). A good majority of people were also told that if you put your dislodged baby tooth under your pillow, a fairy will come and replace it with money, a fat man in a red suit flies around the world commiting B&E in the name of materialism, and some bunnies lay colorful, candy filled eggs once a year. As we all struggle with whatever Websters dictionary means by 'adulting', how do we sort the lies from helpful advice? Today we earn the right to brand them as malicious liars and never speak to them again, or we find a good reason to call and say thank you for the great advice.
  
  When our mothers and grandmothers said that an apple a day keeps the doctor away, they may not have known about the relationship between correlation and causation. They may have just seen healthy people eating lots of apples or maybe they realized that when they spent more money on produce at their local store, medical expenditures went down. 
  
  The question remains, Where are they getting all of this crap? Why did they specifically say apples? and which doctors were they talking about? My shrink? General practitioners? Anyone with a PHD? Cancer doctors? 
  
  This "study" will put take old adage "an apple a day keeps the doctor away" and put it on trial. The first step will be to break this phrase down to its principle parts and define them. 
  
  What will an apple/day mean?
  Fruit consumed kgs/capita/year, cal from plant protein, calories from animal protein, calories from fat
  
  What does keep the doctor away mean? 
  It can mean dalys, cancer prevalence, depressive disorders, life expectancy.
  
My first question is: is our data normalized? Here I take steps to normalize the data from the 
columns where the skewness coefficient is not within the range (-0.6:0.6). I normalize the 
data by applying the sqrt() function and overwriting those same columns with excessive skew. 

```{r}
var <- select(df, -c(entity, total_pop, year, continent))
col <- data.frame(names(var))

var_skew <- data.frame(col, apply(var, 2, skewness, na.rm = TRUE)) 
print(var_skew)


skewed_bad <- filter(var_skew, !between(var_skew$apply.var..2..skewness..na.rm...TRUE., -0.6, 0.6))

skewed_bad$names.var.

df2 <- df
df2[,skewed_bad$names.var.] <- df2 %>% 
  select(skewed_bad$names.var.) %>% 
  apply(2, sqrt)

```


Now that my data is normalized, lets compare the best known predictor of life expectancy (GDP) to 
apple production. 
```{r}
df2 %>% 
  filter(year == 2005) %>% 
  ggplot(aes(x = gdp_capita_year, y = life_expectancy/10))+
  geom_point()+
  geom_smooth()

mod <- glm(life_expectancy ~ gdp_capita_year, data = df2)
summary(mod)

```
GDP is statistically significant, however it does have a small impact. Life expectancy changes  0.005 for every increase of 1 from life expectancy. 

Let's compare that to kilograms of apples produced and my other dependent variables:
```{r}
names(df2)
df2 %>% 
  ggplot(aes(x = gdp_capita_year, y = life_expectancy))+
  geom_point()+
  geom_smooth() 

mod1 <-  glm(life_expectancy ~ gdp_capita_year,
             data = df2)

gdp_life <- tidy(mod1)

print(gdp_life)
```
GDP for sure has an effect, albeit a tiny effect, estimated at 0.005 for a change in GDP

Let's measure the effect of each of my independent variables against life expectancy and compile them into one table 

```{r}
names(df2)
#apples are mod2
mod2 <-  glm(life_expectancy ~ kg_apple_prod_capita_year,
             data = df2)
apl_life <- tidy(mod2)
#cal from animal protein is mod3
mod3 <-  glm(life_expectancy ~ cal_frm_animl_prot,
             data = df2)
animl_life <- tidy(mod3)
#cal from plant protein is mod4
mod4 <-  glm(life_expectancy ~ cal_frm_plnt_prot,
             data = df2)
plnt_life <- tidy(mod4)
#cal from fat is mod5
mod5 <-  glm(life_expectancy ~ cal_frm_fat,
             data = df2)
fat_life <- tidy(mod5)
#cal from carbs is mod6
mod6 <-  glm(life_expectancy ~ cal_frm_carbs,
             data = df2)
carbs_life <- tidy(mod6)
#fruit consumer per capit is mod7
mod7 <-  glm(life_expectancy ~ fruit_consumed_kg_pc_year,
             data = df2)
fruit_life <- tidy(mod7)

#full join
a <- full_join(apl_life, fat_life)
b <- full_join(a,plnt_life)
c <- full_join(b,animl_life)
d <- full_join(c, gdp_life)
e <- full_join(d, carbs_life)              
sum <- full_join(e, fruit_life)


sum <- sum %>% 
  filter(term != "(Intercept)") %>% 
  select(term, estimate, p.value)

print(sum)

sum %>% 
  ggplot(aes(x = term, y = estimate)) +
  geom_col()+
  theme(axis.text.x = element_text(angle = 60,
        vjust = 1, hjust = 1))




```
WOW... I was not expecting that. Kilograms of apples produced per capita has a much larger effect than ANY of my other independant variables. Let's visualize this data:
```{r}
df2 %>% 
  ggplot(aes(x = kg_apple_prod_capita_year, y = life_expectancy))+
  geom_point()+
  geom_smooth()

df %>% 
  filter(year == 2019) %>% 
  select(year, life_expectancy) %>% 
  summary(life_expectancy)

```
According to our data, the average life expectancy in 2019 was approximately 76 years. 
How well will production of apples (our strongest correlation to life expectancy) predict whether a person will live at least to 76?
```{r}
df <- df %>% 
mutate("makes_avg" = case_when(life_expectancy >= 76 ~ TRUE,
                        TRUE~FALSE))
mod8<- glm(data = df,
              formula = makes_avg ~ kg_apple_prod_capita_year,
              family = "binomial")

df %>%
     add_predictions(mod8, type = "response") %>%
     ggplot(aes(x = kg_apple_prod_capita_year, y = pred)) +
     geom_smooth()

```


That is a perfect logistical curve if I've ever seen one! The more apples your country produces, the greater your chances of meeting an average life expectancy. 

Overall, production of apples has a relatively large impact on life expectancy. I want to know if this is true for poor, medium, and affluent countries. Here I will divide GDP into 1/3s. The lower third I will classify as poor, the second third will be medium, and the upper third will be affluent. 
To start, I want to see if there are any differences in apple production between poor, medium, and affluent countries. 
```{r}
(max(df$gdp_capita_year, na.rm = TRUE)) * 0.333 #poor < 38258.1
(max(df$gdp_capita_year, na.rm = TRUE)) * 0.666 #medium 38258.1-76516.19
                                                #affluent > 76516.19

df <- df %>% 
  mutate("wealth" = case_when(gdp_capita_year < 38258.1 ~ "poor",
                            gdp_capita_year < 76516.18~ "medium",
                            TRUE ~ "rich"))
df %>% 
  ggplot(aes(x = wealth, y = kg_apple_prod_capita_year))+
  geom_col()

df %>%
     add_predictions(mod8, type = "response") %>%
     ggplot(aes(x = kg_apple_prod_capita_year, y = pred, color = wealth)) +
     geom_smooth()

  
```
According to this data, production of apples per capita has very similar predicting power regardless of financial status! 

Now every good statistician knows that CORRELATION IS NOT CAUSATION. One of statistics golden rules. However we see that some relationship exists between apple production and life expectancy. It may be that apples only grow at some latitudes or climates and along with altitude comes different conditions, such as temperature, precipitation, natural disaster prevalence etc. and different climates or latitudes explain or even cause fluctuations in life expectancy. 




