---
title: "Final Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE, warning = FALSE)
library(tidyverse)
df <- read.csv("merged_data.csv")
```

Does an apple/day keep the doctor away?
  
  What will an apple/day mean?
  Fruit consumed kgs/capita/year, cal from plant protein, calories from animal protein, calories from fat
  
  What does keep the doctor away mean? 
  It can mean dalys, cancer prevalence, depressive disorders, life expectancy.
  
My first question is: is our data normalized? 

```{r}
ind <- data.frame(df$kg_apple_prod_capita_year, df$cal_frm_plnt_prot, df$fruit_consumed_kg_pc_year, df$cal_frm_animl_prot, df$cal_frm_fat)
skewness(df$kg_apple_prod_capita_year)
```



```{r}
df %>% 
  filter(year == 2005) %>% 
  ggplot(aes(x = kg_apple_prod_capita_year))+
  geom_histogram()

  df %>% 
  filter(year == 2005) %>% 
  ggplot(aes(x = cal_frm_plnt_prot))+
  geom_histogram()


df %>% 
  filter(year == 2005) %>% 
  ggplot(aes(x = fruit_consumed_kg_pc_year))+
  geom_histogram()


df %>% 
  filter(year == 2005) %>% 
  ggplot(aes(x = cal_frm_animl_prot))+
  geom_histogram()

df %>% 
  filter(year == 2005) %>% 
  ggplot(aes(x = cal_frm_fat))+
  geom_histogram()


for (i in independant_variable) {
  return(as.list(skewness(i))
}
```
The data appears to be strongly skewed to the left with apples produced, calories from animal protein, and total fruit consumed per year. I am going to normalize my skewed distributions, 

